<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  message = FALSE,
  width = 120,
  warning = FALSE
)
```

The Panama Papers in R
--------------------------

This provides the datasets from the ICIJ Offshore Leaks Database from the Panama Papers. This dataset was constructed by the International Consortium of Investigative Journalists and available [here](https://offshoreleaks.icij.org/pages/database) under the [Creative Commons Attribution-ShareAlike](http://creativecommons.org/licenses/by-sa/3.0/) license. Besides that data, this package is available under GPL-3.

Future versions of this package may soon include other data from the Panama Papers besides the offshore leaks dataset.

### Installation

Install using [devtools](https://github.com/hadley/devtools):

```
devtools::install_github("dgrtwo/rpanama")
```

### Offshore Leaks

There are five main datasets that this package provides. First is information on the Entities, Intermediaries, Officers, and Addresses from the offshore leaks dataset (see [here](https://offshoreleaks.icij.org/pages/about#terms_definition) for the definitions of each):

```{r}
library(rpanama)
library(dplyr)

Entities
Intermediaries
Officers
Addresses
```

These each make up nodes in a network. The `all_edges` dataset contains connections between these, including which entities have which offshore accounts.

```{r}
all_edges

all_edges %>%
  count(rel_type, sort = TRUE)
```

Each of the five above datasets comes directly from the CSVs released by the ICIJ [here](https://offshoreleaks.icij.org/pages/database).

### Example

We could find which countries have the most offshore entities (note that there are multiple countries split by `;`):

```{r}
library(tidyr)
library(stringr)

most_common_countries <- Entities %>%
  select(node_id, countries) %>%
  unnest(country = str_split(countries, ";")) %>%
  count(country, sort = TRUE)

most_common_countries
```

We may also find inter-country intermediary relationships were most common. We could do this by joining the `Intermediaries` data with the `all_edges` data and then the `Entities` data:

```{r}
entity_countries <- Entities %>%
  unnest(entity_country = str_split(countries, ";"),
         entity_code = str_split(country_codes, ";")) %>%
  select(node_id, entity_country, entity_code)

connections <- Intermediaries %>%
  unnest(intermediary_country = str_split(countries, ";"),
         intermediary_code = str_split(country_codes, ";")) %>%
  inner_join(all_edges, by = c(node_id = "node_1")) %>%
  inner_join(entity_countries, by = c(node_2 = "node_id")) %>%
  filter(rel_type == "intermediary of",
         intermediary_country != entity_country) %>%
  count(intermediary_country, entity_country, intermediary_code, entity_code) %>%
  ungroup() %>%
  arrange(desc(n))

connections
```

We could even put this on a map:

```{r}
library(rworldmap)
library(geosphere)

country_centers <- getMap()@data %>%
  tbl_df() %>%
  select(code = ISO_A3, longitude = LON, latitude = LAT)

great_circles <- connections %>%
  filter(n > 100) %>%
  mutate(connection = row_number()) %>%
  select(intermediary_code, entity_code, n, connection) %>%
  gather(type, code, contains("code")) %>%
  inner_join(country_centers, by = "code") %>%
  group_by(connection, n) %>%
  arrange(desc(type)) %>%
  filter(n() == 2) %>%
  do(as.data.frame(gcIntermediate(c(.$longitude[1], .$latitude[1]),
                                  c(.$longitude[2], .$latitude[2]))))

library(ggplot2)

great_circles %>%
  ggplot(aes(lon, lat, group = connection, alpha = n)) +
  borders("world", alpha = .5) +
  geom_path(arrow = arrow(length = unit(.1, "inches")), color = "red") +
  theme_void() +
  #scale_size_continuous(trans = "log", range = c(.1, 1)) +
  coord_fixed(2, xlim = c(-180, 180), ylim = c(-55, 90)) +
  scale_color_gradient2(low = "white", high = "red", trans = "log") +
  theme(legend.position = "none") +
  ggtitle("Most common offshore entity relationships")
```
